%-------------------------
% Resume in Latex
% Author : Rakesh Babu
% Website: https://github.com/itsrakesh/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Rakesh Babu}} \\
  \small{Male, 28 Years} &  \href{mailto:itsrakesh13@gmail.com}{itsrakesh13@gmail.com }\textbar{ +91-9958843603} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology}{Allahabad, India}
      {Master in Technology in Software Engineering;  CGPA: 8.56/10}{Aug 2012 -- Jun 2014}
    \resumeSubheading
      {RCC Institute of Information Technology}{Kolkata, India}
      {Bachelor of Engineering in Information Technology;  CGPA: 8.14/10 }{Jul 2007 -- Jun 2011}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Myntra Jabong}{Gurgaon, India}
      {Senior Software Developer Engineer}{June 2017 - Present}
      \resumeItemListStart
        \resumeItem{Hystrix circuit breaker}
          {Intelligent Transaction System. Bin based routing to PG's available in an intelligent manner.}
        \resumeItem{Loyalty Points}
          {Loyalty Points is an payment instrument used for marketing promotion and referral reward. Build Admin Panel for upload batch process, handle refund.}
         \resumeItem{Checkout/Payment}
          {Checkout optimizations, PG’s integration, Payment Transaction Refund and Return. Multitenant System Design for checkout instruments for Myntra and Jabong both.}
      \resumeItemListEnd

    \resumeSubheading
      {Tolexo}{Noida, India}
      {Senior Software Developer Engineer}{Oct 2015 - Jun 2017}
      \resumeItemListStart
        \resumeItem{Data Migration}
          {Product and Catalog Data migration from relational Mysql database to Mongo database.}
        \resumeItem{Catalog and Product Upload System}
          {Setting up the back-end service for uploading Category and Product data and save it to the database.}
        \resumeItem{Redesign Payment}
          {Checkout and Payment module redesign and integration with aggregator service of indiamart.}
        \resumeItem{Card/Order Service}
          {Optimization's to acheive high throughput in cart service,  order API and  cronjobs}
      \resumeItemListEnd

    \resumeSubheading
      {Lenskart}{Delhi, India}
      {Software Engineer}{Jun 2014 - Oct 2015}
      \resumeItemListStart
        \resumeItem{Lenskart Wallet}
          {Design and develop Lenskart Wallet named Franchise Credit to support Franchise store transactions.}
        \resumeItem{Optical store}
          {Dashboard feature to show all stores, it's details and it’s geo location at a place.}
          \resumeItem{Automation}
          {Automate the process of marketing campaign to generate customer specific gift coupon in multiple denominations.}
          \resumeItem{Admin Panel}
          {Developed an interface to enter the eye sight power and prescriptions and the backend API to get It’s detail.}
     \resumeItemListEnd
    \resumeSubheading
      {Cognizant}{Kolkata, India}
      {Programmer Analyst}{Jan 2012 - Aug 2012}
      \resumeItemListStart
        \resumeItem{BI Tools}
          {Worked on BI Tools like informatica, MicroStrategy to prepare ETL Workflow and transformation.}
        \resumeItem{Data Warehouse}
          {Training in data warehouse and data mining concepts. Analyzed large volume data and retrieve metadata by doing business intelligence with standard BI Tools.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
     \resumeItem{Languages}{Golang, Java, Php, JavaScript}
     \resumeItem{Databases}{ MySql, Mongo, Cassandra, Redis, CouchDB}
     \resumeItem{Tools}{GIT, JIRA, NewRelic, Docker, Datadog, Grafana}
 \resumeSubHeadingListEnd
 
%-------------------------------------------

%--------ACHIEVEMENTS & EXTRA CURRICULAR ACTIVITIES------------
\section{Acheivements/Curricular Activities}
\begin{itemize}[leftmargin=4 mm] \setlength{\itemsep}{0pt}
     \item Training and Placement coordinator at MNNIT Allahabad.
     \item Awarded as a rock star employee at Tolexo.
     \item Winner of blogging competition among all fresher’s in Cognizant Technology solution at Kolkata.
      \item Won lecture and essay competition held at school.
\end{itemize}
 
%-------------------------------------------
\end{document}
